Numerical simulation of the dynamics of the artificial heart valve

### 2015-05-08 citech-2015/Paper-template/paper.tex
Working on the text for citech paper

\section{Mathematicla formulation of the problem}

>>>>

\section{Mathematical formulation of the problem}

We consider a nonstationary problem of blood flow inside vessel with valve. Blood consists of the plasma and formed elements, which are approximately
45\% of the entire volume \cite{karro}. Vessel walls and valve leaflets consists of the large number of thin collagen fibers, they are flexibe
and can change their form depending on the fluid flow. The aortic valve, which are placed at the outlet from the left ventricle to the aorta, and provide
one-way movement of the blood, can be an example of this kind of systems (see Fig. \ref{fig:aortic_valve_example}):

\begin{figure}
\centering
\includegraphics[height=6.2cm]{images/aorta_scheme.png}
\caption{Aortic valve and its location inside heart}
\label{fig:aortic_valve_example}
\end{figure}
